---
title: "TIME_Behavioural_Analysis"
output: 
  pdf_document: 
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Confirmatory Analysis 
```{r Participant Exclusion Analysis with BootStrapping,message=FALSE, warning=FALSE, out.width="55%"}
# Load libraries and set path ------------------------------------------------
library(lme4);library(car); 
library(ggplot2);library(emmeans)
library(tinytex);library(MKinfer)

# Arrange the data --------------------------------------------------------

# Set the seed for reproducibility
set.seed(13021996)

# get data folder path
DataFolder <- paste(getwd(),"/CombinedMemoryData", sep = "")

# List of subject names
subjects <- c("Sub_01", "Sub_02", "Sub_03", "Sub_04", "Sub_05", "Sub_06", "Sub_07",
              "Sub_08", "Sub_09", "Sub_10", "Sub_11", "Sub_12", "Sub_13", "Sub_14",
              "Sub_15", "Sub_16", "Sub_17", "Sub_18", "Sub_19", "Sub_20", "Sub_21",
              "Sub_22", "Sub_23", "Sub_24", "Sub_25", "Sub_26", "Sub_27", "Sub_28",
              "Sub_29", "Sub_30", "Sub_31", "Sub_32")

# Initialize data frame
TIME_Data <- data.frame()

# Loop through subjects
for (iSub in 1:length(subjects)) {
  # Define file name
  File_pattern <- paste(subjects[iSub], "_memory.csv", sep = "")
  
  # Read the CSV file
  sub_data <- read.csv(file.path(DataFolder, File_pattern), header = TRUE)
  
  # Combine the subject's runs with the overall combined data
  TIME_Data <- rbind(TIME_Data, sub_data)
}

# Participant Exclusion w/ Permutation ------------------------------------

# Calculate the mean accuracy for each subject
Mean_Accs <- tapply(TIME_Data$Accuracy, TIME_Data$ParticipantID , mean)

# parameters
nIterations <- 10000
Subs <- 1:length(subjects)

for (iSub in Subs) {
  
  NullDist <- data.frame(Acc=rep(NA,nIterations))
  
  for (i in 1:nIterations) {
    # Generate 192 random responses between 1 and 4
    Responses <- TIME_Data[TIME_Data$ParticipantID == iSub, "Response"]
    
    # Generate 192 random answers between 1 and 4
    Answers <- sample(TIME_Data[TIME_Data$ParticipantID == iSub, "CorrectKey"])
    
    NullDist[i,1] <- ((sum(Responses == Answers))/length(Responses))*100
  }
  
  # Sort distribution
  SortedNullDist <- NullDist[order(NullDist$Acc),]
  Significance_Threshold <- SortedNullDist[length(SortedNullDist)-nIterations*.05]
  
  # print(ggplot(NullDist, aes(x=Acc)) + geom_density(fill="gray") +
  #         geom_vline(aes(xintercept = Mean_Accs[as.character(iSub)]*100),
  #                    color="green", linetype="dashed", linewidth=1)+
  #         geom_vline(aes(xintercept = Significance_Threshold),
  #                    color="red", linetype="dashed", linewidth=1)+
  #         ggtitle(paste("Sub -", as.character(iSub))))
  
  if ((Mean_Accs[as.character(iSub)])*100 <= Significance_Threshold) {
    print(c(iSub,' is at chance-level!!!'))
  }
}

```

```{r Logistic Mixed-effects Model, warning=FALSE, out.width="55%"}
# Logistic Mixed-effects Model --------------------------------------------

# recode variable types
TIME_Data$Condition <- as.factor(TIME_Data$Condition)
TIME_Data$ParticipantID <- as.factor(TIME_Data$ParticipantID)
TIME_Data$ClipID <- as.factor(TIME_Data$ClipID)

# registered model
TIME.model = glmer(Accuracy ~ Condition + (1|ClipID) + (1|ParticipantID),
                   data=TIME_Data, family = binomial)

# summary and plotting
Anova(TIME.model)
summary(TIME.model)

ggplot(TIME_Data,aes(x=Condition,y=Accuracy))+
  stat_summary(fun.data=mean_cl_boot,size=2)

TIME.emm.s <- emmeans(TIME.model,"Condition")
#pairs(TIME.emm.s)

# Conditions within TIME.emm.s ordered: AsyncTheta, NoFlicker, SyncDelta, SyncTheta
# Planned comparisons for correction .05/3
(out1 <- contrast(TIME.emm.s, list(SyncTheta.vs.NoFlicker  = c(0, -1, 0, 1))))
(out2 <- contrast(TIME.emm.s, list(SyncTheta.vs.AsyncTheta = c(-1, 0, 0, 1))))
(out3 <- contrast(TIME.emm.s, list(SyncTheta.vs.SyncDelta  = c(0, 0, -1, 1))))

(EffectSizes <- eff_size(TIME.emm.s, sigma = sigma(TIME.model), edf = df.residual(TIME.model), method = "pairwise"))

```
### Contrast Summary:  

* SyncTheta vs. NoFlicker p-value = `r  format(summary(out1)$p.value, scientific = FALSE)` H1 = `r (summary(out1)$p.value) < .05/3`  

* SyncTheta vs. AsyncTheta p-value = `r  format(summary(out2)$p.value, scientific = FALSE)` H1 = `r (summary(out2)$p.value) < .05/3`  

* SyncTheta vs. SyncDelta p-value = `r  format(summary(out3)$p.value, scientific = FALSE)` H1 = `r (summary(out3)$p.value) < .05/3`  

*p-critical = .05/3


```{r Data plotting, warning=FALSE, out.width="55%"}

plot(TIME.emm.s,comparisons = TRUE) +
  ggtitle("Estimated Marginal Means")

EMFrame <- data.frame(TIME.emm.s)
EMFrame$Condition = factor(EMFrame$Condition, levels = c("SyncTheta", "NoFlicker", "AsyncTheta", "SyncDelta"), ordered = FALSE)

ggplot(EMFrame, aes(x = Condition, y = emmean, color = Condition)) +
  geom_point() +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.2) +
  labs(title="Estimated Marginal Means per Condition", x = "Condition", y = "EMMs")

ggsave("Emmeans.tiff", dpi = 300)
  
# Calculate the mean accuracy for each subject
sub_means <- tapply(TIME_Data$Accuracy, TIME_Data$ParticipantID , mean)
# Calculate accuracy for each subject and condition
pSub_pCondition_acc <- aggregate(Accuracy ~ ParticipantID + Condition, data = TIME_Data, mean)
pSub_pCondition_acc$Condition = factor(pSub_pCondition_acc$Condition, levels = c("SyncTheta", "NoFlicker", "AsyncTheta", "SyncDelta"), ordered = FALSE)

ggplot(pSub_pCondition_acc, aes(x = Condition, y = Accuracy, fill = Condition)) +
  geom_violin(trim=FALSE)+
  geom_point(size = 2, color = "gray") +
  geom_line(aes(group = ParticipantID), color = "gray", alpha = .7) +
  labs(title="Trial-Averaged Means per Conditions", x = "Condition", y = "Accuracy") + 
  stat_summary(fun.pSub_pCondition_acc = "mean_cl_normal", geom = "errorbar", width = 0.1, color = "black", conf_level = 0.95) +
  stat_summary(fun.pSub_pCondition_acc = "mean", geom = "point", size = 2, color = "black")
ggsave("Rawmeans.tiff", dpi = 300)

# plot individual data
# for (iSub in Subs) {
#   
#   participant_data <- subset(pSub_pCondition_acc, ParticipantID == iSub)
#   
#   print(ggplot(participant_data, aes(x = Condition, y = Accuracy, group = 1, fill = Condition)) +
#           geom_line(color = "Black", alpha = 0.5) +
#           labs(title = paste("Sub -", iSub), x = "Condition", y = "Accuracy") +
#           scale_y_continuous(limits = c(.20, .80)) +
#           theme_minimal())
#   
# }
```

```{r Trial-averaged test with bootstrapping, warning=FALSE, out.width="55%"}

# Calculate means
(mAll <- mean(pSub_pCondition_acc$Accuracy)*100)
(sdAll <- sd((sub_means)*100))
(mSyncTheta <- mean(pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition=="SyncTheta"])*100)
(mNoFlicker <- mean(pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition=="NoFlicker"])*100)
(mAsyncTheta <- mean(pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition=="AsyncTheta"])*100)
(mSyncDelta <- mean(pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition=="SyncDelta"])*100)

SyncTheta_NoFlicker <- pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition=="SyncTheta"]*100-
  pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition == "NoFlicker"]*100
SyncTheta_AsyncTheta <- pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition=="SyncTheta"]*100-
  pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition == "AsyncTheta"]*100
SyncTheta_SyncDelta <- pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition=="SyncTheta"]*100-
  pSub_pCondition_acc$Accuracy[pSub_pCondition_acc$Condition == "SyncDelta"]*100

(SyncTheta_NoFlicker_out <- boot.t.test(SyncTheta_NoFlicker,
                                        alternative = c("two.sided", "less", "greater"), 
                                        mu = 0, paired = FALSE, var.equal = FALSE,
                                        conf.level = 0.95, R = 10000, symmetric = FALSE))
abs(mean(SyncTheta_NoFlicker)/sd(SyncTheta_NoFlicker)) # Cohen's d 


(SyncTheta_AsyncTheta_out <- boot.t.test(SyncTheta_AsyncTheta,
                                         alternative = c("two.sided", "less", "greater"),
                                         mu = 0, paired = FALSE, var.equal = FALSE,
                                         conf.level = 0.95, R = 10000, symmetric = FALSE))
abs(mean(SyncTheta_AsyncTheta)/sd(SyncTheta_AsyncTheta)) # Cohen's d 

(SyncTheta_SyncDelta_out <- boot.t.test(SyncTheta_SyncDelta,
                                        alternative = c("two.sided", "less", "greater"),
                                        mu = 0, paired = FALSE, var.equal = FALSE,
                                        conf.level = 0.95, R = 10000, symmetric = FALSE))
abs(mean(SyncTheta_SyncDelta)/sd(SyncTheta_SyncDelta)) # Cohen's d 

```


### Trial-averaged Contrast Summary:  

* SyncTheta vs. NoFlicker p-value = `r  as.character(SyncTheta_NoFlicker_out$p.value)` H1 = `r SyncTheta_NoFlicker_out$p.value < .05/3`  

* SyncTheta vs. AsyncTheta p-value = `r  as.character(SyncTheta_AsyncTheta_out$p.value)` H1 = `r SyncTheta_AsyncTheta_out$p.value < .05/3`  

* SyncTheta vs. SyncDelta p-value = `r  as.character(SyncTheta_SyncDelta_out$p.value)` H1 = `r SyncTheta_SyncDelta_out$p.value < .05/3`  

*p-critical = .05/3

```{r Synchrony Discrimination Task, warning=FALSE, out.width="55%"}

# Arrange long-format data
# get data folder path
SyncDataFolder <- paste(getwd(),"/SyncDiscData", sep = "")

# List of subject names
subjects <- c("Sub_01", "Sub_02", "Sub_03", "Sub_04", "Sub_05", "Sub_06", 
              "Sub_09", "Sub_10", "Sub_11", "Sub_14", "Sub_15", "Sub_17", 
              "Sub_19", "Sub_20", "Sub_22", "Sub_23", "Sub_24", "Sub_25", 
              "Sub_27", "Sub_29","Sub_30", "Sub_31","Sub_32")
nSub <- length(subjects)

# Initialize vectors to store results
nHits_pSub <- rep(NA, nSub)
HitRate_pSub <- rep(NA, nSub)
nFAs_pSub <- rep(NA, nSub)
FARate_pSub <- rep(NA, nSub)
Dprime_pSub <- rep(NA, nSub)
Sync_subnums <- rep(NA, nSub)

# Loop over subjects
for (iSub in 1:nSub) {
  
  # List all files in the current directory that match the pattern
  file_name <- list.files(path = SyncDataFolder, pattern = subjects[iSub])
  
  SyncData <- read.csv(file.path(SyncDataFolder, file_name), header = TRUE)
  
  # Calculate Hit Rate
  nHits_pSub[iSub] <- sum(SyncData$SyncRating == 1 & SyncData$Accuracy == 1)
  HitRate_pSub[iSub] <- nHits_pSub[iSub] / sum(SyncData$SyncRating == 1)
  
  # Calculate False Alarm Rate
  nFAs_pSub[iSub] <- sum(SyncData$SyncRating == 2 & SyncData$Accuracy == 0)
  FARate_pSub[iSub] <- nFAs_pSub[iSub] / sum(SyncData$SyncRating == 2)
  
  # Calculate d-prime
  Dprime_pSub[iSub] <- qnorm(HitRate_pSub[iSub]) - qnorm(FARate_pSub[iSub])
  Sync_subnums[iSub] <- SyncData$ParticipantID[iSub]
}

# Create a data frame
DprimeData <- data.frame(ParticipantID = as.factor(Sync_subnums), Dprime = Dprime_pSub)

# significance test
(DPrime_out <- boot.t.test(DprimeData$Dprime, alternative = c("two.sided", "less", "greater"),
                           mu = 0, paired = FALSE, var.equal = FALSE, conf.level = 0.95,
                           R = 10000, symmetric = FALSE))

# Create a violin plot
ggplot(data = DprimeData, aes(x = 0, y = Dprime)) +
  geom_violin(width=1, fill = "orange", color = "black", alpha = 0.5) +
  scale_x_discrete( ) +
  geom_point(position = "jitter",size = 3, color = "gray") +
  labs(title = "D-prime Scores",
       x = "Participants",
       y = "D-prime")

```
## Exploratory Analysis 

```{r Rating Analysis, warning=FALSE, out.width="55%"}
# Rating as random intercept----------------------

# Calculate the mean accuracy for each subject
sub_Ratingmeans <- tapply(TIME_Data$Rating, TIME_Data$ParticipantID , mean)
# Calculate accuracy for each subject and condition
pSub_pCondition_rating <- aggregate(Rating ~ ParticipantID + Condition, data = TIME_Data, mean)
pSub_pCondition_rating$Condition = factor(pSub_pCondition_rating$Condition, levels = c("SyncTheta", "NoFlicker", "AsyncTheta", "SyncDelta"), ordered = FALSE)

ggplot(pSub_pCondition_rating, aes(x = Condition, y = Rating, fill = Condition)) +
  geom_violin(trim=FALSE)+
  geom_point(size = 2, color = "gray") +
  geom_line(aes(group = ParticipantID), color = "gray", alpha = .7) +
  labs(title="Trial-Averaged Means per Conditions", x = "Condition", y = "Rating") + 
  stat_summary(fun.pSub_pCondition_rating = "mean_cl_normal", geom = "errorbar", width = 0.1, color = "black", conf_level = 0.95) +
  stat_summary(fun.pSub_pCondition_rating = "mean", geom = "point", size = 2, color = "black")

# cor(TIME_Data$Rating, TIME_Data$Accuracy)
# 
# ggplot(TIME_Data, aes(x=Rating, y=Accuracy)) + 
#   geom_point()+
#   geom_smooth(method=lm)

# Model with Rating as random effect
TIME.modelofRating = glmer(Rating ~ Condition + (1|ClipID) + (1|ParticipantID),
                   data=TIME_Data)
Anova(TIME.modelofRating)
summary(TIME.modelofRating)

TIME.emm.sofRating <- emmeans(TIME.modelofRating,"Condition")
#pairs(TIME.emm.s)

# Conditions within TIME.emm.s ordered: AsyncTheta, NoFlicker, SyncDelta, SyncTheta
# Planned comparisons for correction .05/3
(out1 <- contrast(TIME.emm.sofRating, list(SyncTheta.vs.NoFlicker  = c(0, -1, 0, 1))))
(out2 <- contrast(TIME.emm.sofRating, list(SyncTheta.vs.AsyncTheta = c(-1, 0, 0, 1))))
(out3 <- contrast(TIME.emm.sofRating, list(SyncTheta.vs.SyncDelta  = c(0, 0, -1, 1))))

(EffectSizes <- eff_size(TIME.emm.sofRating, sigma = sigma(TIME.modelofRating),
                         edf = df.residual(TIME.modelofRating), method = "pairwise"))



TIME_Data$RatingFactor = as.factor(TIME_Data$Rating)

# Model with Rating as random effect
TIME.modelwRating = glmer(Accuracy ~ Condition*poly(RatingFactor,2) + (1|ClipID) + (1|ParticipantID),
                   data=TIME_Data, family = binomial)

Anova(TIME.modelwRating)
summary(TIME.modelwRating)

TIME.emm.swRating <- emmeans(TIME.modelwRating,"Condition")

# Conditions within TIME.emm.s ordered: AsyncTheta, NoFlicker, SyncDelta, SyncTheta
# Planned comparisons for correction .05/3
(out1 <- contrast(TIME.emm.swRating, list(SyncTheta.vs.NoFlicker  = c(0, -1, 0, 1))))
(out2 <- contrast(TIME.emm.swRating, list(SyncTheta.vs.AsyncTheta = c(-1, 0, 0, 1))))
(out3 <- contrast(TIME.emm.swRating, list(SyncTheta.vs.SyncDelta  = c(0, 0, -1, 1))))

(EffectSizes <- eff_size(TIME.emm.swRating, sigma = sigma(TIME.modelwRating),
                         edf = df.residual(TIME.modelwRating), method = "pairwise"))

RatingEMFrame <- data.frame(TIME.emm.swRating)
RatingEMFrame$Condition = factor(RatingEMFrame$Condition, levels = c("SyncTheta", "NoFlicker", "AsyncTheta", "SyncDelta"), ordered = FALSE)

ggplot(RatingEMFrame, aes(x = Condition, y = emmean, color = Condition)) +
  geom_point() +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.2) +
  labs(title="Estimated Marginal Means per Condition", x = "Condition", y = "EMMs")

plot(TIME.emm.swRating, comparisons = TRUE) +
  ggtitle("Estimated Marginal Means")

```
```{r Block analysis, warning=FALSE, out.width="55%"}

# filter data to keep only first blocks
FirstBlockOnly <- TIME_Data[TIME_Data$BlockNumber == 1, ]

FirstBlockOnly.model = glmer(Accuracy ~ Condition + (1|ClipID) + (1|ParticipantID),
                   data=FirstBlockOnly, family = binomial)

# summary and plotting
Anova(FirstBlockOnly.model)
summary(FirstBlockOnly.model)

ggplot(FirstBlockOnly,aes(x=Condition,y=Accuracy))+
  stat_summary(fun.data=mean_cl_boot,size=2)

FirstBlockOnly.emm.s <- emmeans(FirstBlockOnly.model,"Condition")
#pairs(TIME.emm.s)

# Conditions within TIME.emm.s ordered: AsyncTheta, NoFlicker, SyncDelta, SyncTheta
# Planned comparisons for correction .05/3
(out1 <- contrast(FirstBlockOnly.emm.s, list(SyncTheta.vs.NoFlicker  = c(0, -1, 0, 1))))
(out2 <- contrast(FirstBlockOnly.emm.s, list(SyncTheta.vs.AsyncTheta = c(-1, 0, 0, 1))))
(out3 <- contrast(FirstBlockOnly.emm.s, list(SyncTheta.vs.SyncDelta  = c(0, 0, -1, 1))))

(EffectSizes <- eff_size(FirstBlockOnly.emm.s, sigma = sigma(FirstBlockOnly.model), 
                         edf = df.residual(FirstBlockOnly.model), method = "pairwise"))

# Block and Condition interaction model
TIME.modelBlock = glmer(Accuracy ~ Condition*poly(BlockNumber,2) + (1|ClipID) + (1|ParticipantID),
                   data=TIME_Data, family = binomial)

Anova(TIME.modelBlock)
summary(TIME.modelBlock)

```
```{r Participant Exclusion based on Theta, warning=FALSE, out.width="55%"}

# Calculate the mean accuracy for each subjects' theta conditions
ThetaTIME_Data <- TIME_Data[TIME_Data$Condition == "SyncTheta" | TIME_Data$Condition == "AsyncTheta",]
ThetaMean_Accs <- tapply(ThetaTIME_Data$Accuracy, ThetaTIME_Data$ParticipantID , mean)

for (iSub in Subs) {

  NullDist <- data.frame(Acc=rep(NA,nIterations))

  for (i in 1:nIterations) {
    # Generate 192 random responses between 1 and 4
    Responses <- TIME_Data[TIME_Data$ParticipantID == iSub, "Response"]

    # Generate 192 random answers between 1 and 4
    Answers <- sample(TIME_Data[TIME_Data$ParticipantID == iSub, "CorrectKey"])

    NullDist[i,1] <- ((sum(Responses == Answers))/length(Responses))*100
  }

  # Sort distribution
  SortedNullDist <- NullDist[order(NullDist$Acc),]
  Significance_Threshold <- SortedNullDist[length(SortedNullDist)-nIterations*.05]

  if ((ThetaMean_Accs[as.character(iSub)])*100 <= Significance_Threshold) {
    print(c(iSub,' is at chance-level!!!'))
  }

}

excludedTIME_data <- TIME_Data[!(TIME_Data$ParticipantID %in% c(2, 12, 14)),]

excludedTIME.model = glmer(Accuracy ~ Condition + (1|ClipID) + (1|ParticipantID),
                   data=excludedTIME_data, family = binomial)

Anova(excludedTIME.model)
summary(excludedTIME.model)

ggplot(excludedTIME_data,aes(x=Condition, y=Accuracy))+
  stat_summary(fun.data=mean_cl_boot, size=2)+
  labs(title = "Trial-averaged Accuracies per Condition 
       (With participant exclusions (3) from theta conditions' accuracies)")

excludedTIME.emm.s <- emmeans(excludedTIME.model,"Condition")

# Conditions within TIME.emm.s ordered: AsyncTheta, NoFlicker, SyncDelta, SyncTheta
# Planned comparisons for correction .05/3
(out1 <- contrast(excludedTIME.emm.s, list(SyncTheta.vs.NoFlicker  = c(0, -1, 0, 1))))
(out2 <- contrast(excludedTIME.emm.s, list(SyncTheta.vs.AsyncTheta = c(-1, 0, 0, 1))))
(out3 <- contrast(excludedTIME.emm.s, list(SyncTheta.vs.SyncDelta  = c(0, 0, -1, 1))))

```
```{r Dprime & Accuracy correlation, warning=FALSE, out.width="55%"}

# select the participants with Dprime
TIME_DatawDprime <- pSub_pCondition_acc[pSub_pCondition_acc$ParticipantID %in% c(Sync_subnums),]

Theta_means <- aggregate(Accuracy ~ Condition*ParticipantID, data = TIME_DatawDprime, FUN = mean)
STheta_means <- Theta_means[Theta_means == "SyncTheta",]
ATheta_means <- Theta_means[Theta_means == "AsyncTheta",]
TIMEEffect <- STheta_means$Accuracy - ATheta_means$Accuracy

cor(DprimeData$Dprime, TIMEEffect, method = "pearson")
cor.test(DprimeData$Dprime, TIMEEffect, method = "pearson")

DprimewTIME <- data.frame(DPrime = DprimeData$Dprime, TIMEEffect)

ggplot(DprimewTIME, aes(x=DPrime, y=TIMEEffect)) +
  geom_point()+
  geom_smooth(method=lm)

```